Abstract

### 2025-06-02 output/Letter_to_editor.Rmd
Make minor changes to letter to editor
Avoids redundancies

Please find attached the updated version of our manuscript
*"A generalized definition of multidimensional item response theory
parameters"*.
We hope that this new version lives up to the expectations of
the action editor and the reviewers;
we have put as much effort as we have been able to address all the comments and
suggestions, which we believe have helped improve the quality of our paper.
However, we acknowledge we may not have resolved satisfactorily all the action
editor's and reviewers' concerns.
Therefore, we would kindly ask you to forward to them our good will
and predisposition to address any further comments or suggestions,
or clarify futher on the previous ones.

We thank you in advance for considering our reviewed manuscript.
Please feel free to contact us again at my aforementioned email address
(dvmorillo@psi.uned.es).
We will be happy to address any further comments or suggestions
the action editor or the reviewers may deem necessary.

>>>>

Please find attached the updated version of our manuscript
*"A generalized definition of multidimensional item response theory
parameters"*.
We hope that this new version lives up to the expectations of
the action editor and the reviewers;
we have put as much effort as we have been able to address all the comments and
suggestions, which we believe have helped improve the quality of our paper.
You will find our thorough responses in the document attached to this letter.
However, we acknowledge we may not have resolved satisfactorily all the action
editor's and reviewers' concerns.
Therefore, we would kindly ask you to forward to them our good will
and predisposition to address any other comments or suggestions,
or clarify further on the previous ones.

We thank you in advance for considering our reviewed manuscript.
Please feel free to contact us again at my aforementioned email address
(dvmorillo@psi.uned.es).
We will be happy to address any additional comments or suggestions
the action editor or the reviewers may deem necessary.
